Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-24 msr/msr2011.tex
expanded topic modeling defn by a line

One challenge for software maintenance is to identify the reasons behind software development activities. Identifying these reasons provides insight into \emph{why} certain changes were made. Topic modeling is a machine learning technique which creates multinomial distributions over words from a text corpus. Topic models are useful in software maintenance because they summarize the key concepts in a corpus, such as source code, commit comments, or email, by identifying statistically co-occuring words. Among other uses, it can quickly give developers an overview of where activity occurred, and gives managers or maintainers a sense of project history. For example, a topic extracted from a set of commit logs might be \emph{ ``listener change remove add fire''}.  A major challenge for topic modeling is to accurately identify the summary label for a topic (in the previous case, perhaps \emph{``event-handling''}). 
Current approaches are manual: they rely on human expertise to recognize the appropriate label. Furthermore, to date the results of topic modeling are project specific, and not generalizable. This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

@@

Concrete applications of topics and \emph{labelled topic extraction}
range from project dashboards to annotating software artifacts with
NFR-related tags such as revisions and bug reports. 
Project dashboard are typically employed by managers and are used to
provide quick summaries of a the efforts put into a software project,
labelled topic extraction would allow managers to track efforts
related to topics, specifically NFRs.
These techniques also allow the annotation of bug
reports and other software artifacts with the NFRs, such as
portability that they relate to, this would enable querying of bug
reports and artifacts by relevant NFRs. 
For instance one could look
for portability relevant revisions and bug reports.

>>>>

One challenge for software maintenance is to identify the reasons behind software development activities. Identifying these reasons provides insight into \emph{why} certain changes were made. Topic modeling is a machine learning technique which creates multinomial distributions over words from a text corpus. The technique infers the hidden structure of a corpus using posterior inference (the probability of the hidden structure given the data). Topic models are useful in software maintenance because they summarize the key concepts in a corpus, such as source code, commit comments, or email, by identifying statistically co-occuring words. Among other uses, it can quickly give developers an overview of where activity occurred, and gives managers or maintainers a sense of project history. For example, a topic extracted from a set of commit logs might be \emph{ ``listener change remove add fire''}.  A major challenge for topic modeling is to accurately identify the summary label for a topic (in the previous case, perhaps \emph{``event-handling''}). 
Current approaches are manual: they rely on human expertise to recognize the appropriate label. Furthermore, to date the results of topic modeling are project specific, and not generalizable. This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

@@

Concrete applications of topics and \emph{labelled topic extraction}
range from project dashboards to annotating software artifacts such as revisions and bug reports with
NFR-related tags.
Project dashboard are typically employed by managers and are used to
provide quick summaries of the effort put into a software project. In this case, 
labelled topic extraction would allow managers to track effort
related to topics, in this paper, NFRs such as usability.
These techniques also allow the annotation of commit comments
 and other software artifacts with NFRs. This would enable querying of bug
reports and artifacts by relevant NFRs. 
For instance one could look
for usability-relevant revisions and bug reports.
